Project Setup

### 2024-09-13 choose_license.qmd
Rework setup and licensing chapters
Following suggestions by Jonas

Note, that for data you have, at least in principle, the option to apply separate licenses to the individual entries and the collective database. For example, if you were to create a database of artworks by others, those artworks would be licensed individually as chosen by the artists, but the license for the database as a whole could be chosen by you. The latter includes the structure of the database (e.g., the selection of entries and field names) and any sui generis database rights. However, if the content was created by you, we recommend you to choose the same license for both content and database. Metadata, in particular, should always be licensed under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/).

@@

Note, however, that the copyleft licenses we discuss here do not mandate sharing. Copyleft (and attribution) clauses are only triggered if the work is shared [@CC2015]. It is also worth reiterating that these licenses do not restrict the original author(s): They are still permitted to distribute their work under a different license and without sharing the source code.

@@

You may have noticed that we mostly refer to licenses using a name _and_ a version number. This is because the organizations that created the licenses sometimes publish updated versions to accommodate for developments in copyright law and the communities that use the licenses. For example, the Creative Commons licenses (that start with `CC`) were first published in 2002. Since then, the possibility to relicense under compatible licenses has been added ([v3.0](https://creativecommons.org/2007/02/23/version-30-launched/)), a 30-day window to correct license violations has been established to combat [copyleft trolls](https://commons.wikimedia.org/wiki/Commons:Copyleft_trolling), and sui generis database rights are covered explicitly ([v4.0](https://creativecommons.org/version4/)). There are many more [subtle differences between license versions](https://wiki.creativecommons.org/wiki/License_Versions), therefore it is important to indicate which license version exactly one is referring to, as the license of a work does not "update" automatically.

@@

```{.bash filename="Terminal"}
pip install reuse
```

@@

If you want to indicate the license for all files in a particular folder, you can create a filed called `REUSE.toml` and add an `[[annotations]]` table for them:

>>>>

Note, that for data you have, at least in principle, the option to apply separate licenses to the individual entries and the collective database. For example, if you were to create a database of artworks by others, those artworks would be licensed individually as chosen by the artists, but the license for the database as a whole could be chosen by you. The latter includes the structure of the database (e.g., the selection of entries and field names) and any _sui generis_ database rights. However, if the content was created by you, we recommend you to choose the same license for both content and database. Metadata, in particular, should always be licensed under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/).

@@

Note, however, that the copyleft licenses we discuss here do not mandate sharing. Copyleft (and attribution) clauses are only triggered if the work is shared [@CC2015]. This means that if you only use a work internally, you do not need to share your derivative works. It is also worth reiterating that these licenses do not restrict the original author(s): They are still permitted to distribute their work under a different license and without sharing the source code.

@@

You may have noticed that we mostly refer to licenses using a name _and_ a version number. This is because the organizations that created the licenses sometimes publish updated versions to accommodate for developments in copyright law and the communities that use the licenses. For example, the Creative Commons licenses (that start with `CC`) were first published in 2002. Since then, the possibility to relicense under compatible licenses has been added ([v3.0](https://creativecommons.org/2007/02/23/version-30-launched/)), a 30-day window to correct license violations has been established to combat [copyleft trolls](https://commons.wikimedia.org/wiki/Commons:Copyleft_trolling), and _sui generis_ database rights are covered explicitly ([v4.0](https://creativecommons.org/version4/)). There are many more [subtle differences between license versions](https://wiki.creativecommons.org/wiki/License_Versions), therefore it is important to indicate which license version exactly one is referring to, as the license of a work does not "update" automatically.

@@

```{.bash filename="Terminal"}
pipx install reuse
```

@@

If you want to indicate the license for all files in a particular folder, you can create a file called `REUSE.toml` and add an `[[annotations]]` table for them:

### 2024-09-13 setup.qmd
Rework setup and licensing chapters
Following suggestions by Jonas

1. applicable privacy laws (e.g., the GDPR for European citizens),
2. contractual obligations (e.g., with your data provider),
3. copyright of the data and their particular structure, and
4. any sui generis database right.

@@

Purely factual data such as measurements are usually not copyrightable, but literary or artistic works that cross the threshold of originality are. Additionally, in some jurisdictions data can be subject to _sui generis database rights_ which prevent extracting substantial parts of a database. As a consequence, you need to ensure that you own or have authority to share the data with respect to copyright and similar rights, and to license it to others (see "[Choose a License](choose_license.qmd)").
:::

@@

>>>>

1. applicable privacy laws (e.g., the GDPR for European citizens),
2. contractual obligations (e.g., with your data provider),
3. copyright of the data and their particular structure, and
4. any _sui generis_ database right.

@@

Purely factual data such as measurements are usually not copyrightable, but literary or artistic works that cross the threshold of originality are. Additionally, in some jurisdictions data can be subject to _sui generis_ database rights which prevent extracting substantial parts of a database. As a consequence, you need to ensure that you own or have authority to share the data with respect to copyright and similar rights, and to license it to others (see "[Choose a License](choose_license.qmd)").
:::

@@

:::: {#nte-take-copyright-seriously-solution .callout-note collapse="true"}
### Hint for "Take Copyright Seriously"

Have a look at the [about page](about.qmd).
::::
